Hypertension and microbiome

### 2018-12-31 rrbiome.Rmd
Minor

```{r self vs registered medication}
table(dset.species$BP_TREAT, dset.species$ANYDRUG)
```

@@

```{r maaslin plots, fig.width = 10, fig.height = 4, dpi = 300}
source("edgeR_plot_functions.R")

plot_maaslin_heatmap_final(maas.results.df.signf,
                      xlab.text="Genera",
                      beta.maxabs=max(abs(maas.results.df.signf[,'beta'])))

>>>>

```{r self vs registered medication}
table(dset.species$BP_TREAT, dset.species$ANYDRUG) %>% kable
```

@@
